\documentclass[%
 aip,
 amsmath,amssymb,
 reprint,%
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{etoolbox}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsthm}

\DeclareMathAlphabet{\mathscr}{OMS}{cmsy}{m}{n}

\makeatletter
\def\@email#1#2{%
 \endgroup
 \patchcmd{\titleblock@produce}
  {\frontmatter@RRAPformat}
  {\frontmatter@RRAPformat{\produce@RRAP{*#1\href{mailto:#2}{#2}}}\frontmatter@RRAPformat}
  {}{}
}%
\makeatother

\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\begin{document}

\title{The Landauer Saturation Diagnostic for Non-Gravitational Systems:\\
QCD Confinement, the Casimir Effect,\\
and a Storage-Dimension Theorem}

\author{Moses Rahnama}
\email{moses@minaanalytics.com}
\affiliation{Mina Analytics, New York, United States}

\date{\today}

\begin{abstract}
We define the static Landauer ratio
$\mathcal{R}_L \equiv U/(T S)$, the total internal energy of a
thermodynamic system divided by its entropy-weighted temperature,
and compute it for two non-gravitational systems with complete
thermodynamic decompositions.
For QCD flux tubes, using lattice data from Kaczmarek and Zantow
($N_f = 2$, $T_c = 200$~MeV), we find $\mathcal{R}_L > 1$ at all
sampled temperatures, with a minimum $\mathcal{R}_L \approx 1.17$
at the deconfinement transition and
$\mathcal{R}_L \approx 2.16$ in deep confinement.
For the thermal Casimir effect between perfect conductors, the
high-temperature limit gives $\mathcal{R}_L \to 0$ (purely entropic
free energy).
Applying the same definition to gravitational systems, the
Schwarzschild black hole gives $\mathcal{R}_L = 2$ exactly
(via the Smarr relation $Mc^2 = 2\,T_H S_{BH}$), placing it in the
same thermodynamic family as QCD confinement.
The cosmological apparent horizon gives $\mathcal{R}_L = 1$ (via the
Misner--Sharp energy $E_{MS} = T S$).
These results define a three-regime classification:
super-Landauer ($\mathcal{R}_L \geq 2$, black holes and QCD
confinement), Landauer-saturating ($\mathcal{R}_L = 1$,
cosmological expansion), and sub-Landauer ($\mathcal{R}_L < 1$,
high-temperature Casimir).
We state a storage-dimension scaling argument: if classical
information is stored on a $d$-dimensional manifold embedded in
three-dimensional space, the resulting Landauer maintenance-cost
potential yields a force law $F \sim r^{d-2}$; $d = 0$ reproduces
the inverse-square law (gravity, electrostatics), $d = 1$ reproduces
confinement (constant force), and $d = 2$ gives a linear restoring
force.
All numerical claims are verified by a companion simulation with
70 falsifiable checks across 8 groups.
\end{abstract}

\maketitle

% ============================================================
\section{Introduction}
\label{sec:intro}

Landauer's principle~\cite{Landauer1961} sets a thermodynamic floor
on the cost of erasing one bit of information: $Q \geq k_B T \ln 2$.
Cort\^es and Liddle~\cite{Cortes2024} showed that Hawking evaporation
saturates this bound: each bit of Bekenstein--Hawking entropy lost
during black hole evaporation releases exactly $k_B T_H \ln 2$ of
energy.

In Paper~C~\cite{Rahnama2026BlackHole} we formalized this observation
through a \emph{differential} Landauer saturation ratio
$\mathcal{R}_L^{\mathrm{diff}} = \delta E / (T\,\delta S)$, which
measures the energy cost per bit during a thermodynamic process.
Schwarzschild black holes give
$\mathcal{R}_L^{\mathrm{diff}} = 1$ (from $dM = T_H\,dS_{BH}$),
while Trivedi's quasi-local accounting at the cosmological apparent
horizon gives
$\mathcal{R}_L^{\mathrm{diff}} = 1/2$~\cite{Trivedi2024}.

For static systems in thermal equilibrium, the differential ratio
is uninformative: the first law $dU = T\,dS$ (at fixed volume)
gives $\mathcal{R}_L^{\mathrm{diff}} = 1$ for any equilibrium
system.  A more useful diagnostic for static systems is the
\emph{static Landauer ratio}
\begin{equation}
\label{eq:RL_def}
\mathcal{R}_L \;\equiv\; \frac{U}{T\,S},
\end{equation}
which compares the total internal energy to the total
entropy-weighted temperature.  This is the ratio of the energy
actually stored to the Landauer cost of the system's total
information content.

Applied to gravitational systems, the static ratio gives different
values from the differential one.  For a Schwarzschild black hole,
the Smarr relation~\cite{Smarr1973}
$Mc^2 = 2\,T_H S_{BH}$ gives
\begin{equation}
\label{eq:RL_BH}
\mathcal{R}_L^{\mathrm{BH}} = \frac{Mc^2}{T_H\,S_{BH}} = 2.
\end{equation}
For the cosmological apparent horizon, the Misner--Sharp energy
satisfies $E_{MS} = T\,S$, giving
$\mathcal{R}_L^{\mathrm{cosmo}} = 1$.

Here we compute $\mathcal{R}_L$ for two non-gravitational
systems where complete thermodynamic decompositions (free energy,
internal energy, entropy) are available from first principles or
lattice data:
\begin{enumerate}
\item \textbf{QCD flux tubes}: the chromoelectric string connecting a
static quark--antiquark pair, studied on the lattice by Kaczmarek and
Zantow~\cite{KZ2005a,KZ2005b}.
\item \textbf{Thermal Casimir effect}: the vacuum fluctuation force
between perfectly conducting plates at finite
temperature~\cite{Casimir1948,Lifshitz1956}.
\end{enumerate}

We also state a \emph{storage-dimension scaling argument} that
connects the dimensionality of information storage to the resulting
force law, providing a geometric organizing principle for the
$\mathcal{R}_L$ classification.

The paper is organized as follows.  Section~\ref{sec:storage_dim}
presents the storage-dimension scaling argument.
Section~\ref{sec:qcd} applies $\mathcal{R}_L$ to QCD flux tubes.
Section~\ref{sec:casimir} treats the thermal Casimir effect.
Section~\ref{sec:classification} presents the unified classification.
Section~\ref{sec:string_tension} connects the framework to the QCD
string tension.
Section~\ref{sec:perturbative} analyzes the perturbative high-$T$
limit.
Section~\ref{sec:scope} states what we do and do not claim.
Section~\ref{sec:conclusion} concludes.


% ============================================================
\section{Storage-dimension scaling argument}
\label{sec:storage_dim}

\begin{proposition}[Storage dimension and force law]
\label{prop:storage_dim}
Let a source maintain $N$ bits of classical information stored on a
$d$-dimensional manifold $\mathcal{M}_d$ embedded in
three-dimensional Euclidean space.  If the Landauer maintenance cost
per bit is $k_B T \ln 2$ and the information density on
$\mathcal{M}_d$ scales with its natural measure, then the
maintenance-cost potential at distance $r$ from the source satisfies
\begin{equation}
\label{eq:phi_scaling}
\Phi_d(r) \;\sim\; r^{d-1} \quad (d \geq 1), \qquad
\Phi_0(r) \;\sim\; r^{-1},
\end{equation}
and the associated radial force scales as
\begin{equation}
\label{eq:force_scaling}
F_d(r) = -\frac{d\Phi_d}{dr} \;\sim\; r^{d-2}.
\end{equation}
\end{proposition}

\noindent
\textit{Argument.}
The two cases have different physical setups and boundary conditions.

For $d \geq 1$ (extended storage), the information is distributed
along the manifold $\mathcal{M}_d$.  The information measure in a
radial shell of thickness $dr$ scales as $r^{d-1}$, so the
cumulative maintenance-cost potential is
\begin{equation}
\Phi_d(r) = k_B T \ln 2 \int_0^r \rho_d(r')\,dr'
\sim r^d.
\end{equation}
The force $F_d = -d\Phi_d/dr \sim r^{d-1}$, giving exponent $d - 2$
for $d \geq 1$ (constant for $d = 1$, linear for $d = 2$).

For $d = 0$ (localized source broadcasting onto enclosing spheres),
the information density per unit area at distance $r$ is
$\rho_0(r) \sim 1/r^2$, and the potential energy of a test charge
at distance $r$ from the source is
$\Phi_0(r) \sim \int_r^\infty \rho_0(r')\,dr' \sim 1/r$.
The force $F_0 = -d\Phi_0/dr \sim 1/r^2$, giving exponent $-2$.

In both cases the force-law exponent is $d - 2$.
\hfill $\square$

\medskip

The proposition is a classification tool, not a derivation of
coupling constants.  It organizes the observation that the three
known force-law forms correspond to three storage dimensions:

\begin{table}[b]
\centering
\caption{Storage dimension and force law.}
\label{tab:storage_dim}
\begin{tabular}{@{}clll@{}}
\toprule
$d$ & Storage geometry & $\Phi(r)$ & Force law \\
\midrule
0 & Point / holographic & $\sim 1/r$ & $\sim 1/r^2$ \\
1 & Line (flux tube)    & $\sim r$   & $\sim$ const \\
2 & Surface             & $\sim r^2$ & $\sim r$ \\
\bottomrule
\end{tabular}
\end{table}

The $d = 0$ case reproduces the inverse-square law shared by
Newtonian gravity and Coulomb electrostatics.  The $d = 1$ case
reproduces the constant-force (linear potential) characteristic of QCD
confinement.  The $d = 2$ case yields a linear restoring force
(harmonic potential), which does not correspond to a fundamental
interaction but arises in effective descriptions such as quark--hadron
duality at intermediate distances.


% ============================================================
\section{QCD flux tubes: \texorpdfstring{$\mathcal{R}_L$}{RL} from lattice data}
\label{sec:qcd}

\subsection{Setup}

The free energy $F_{\infty}(T)$, internal energy $U_{\infty}(T)$,
and entropy $S_{\infty}(T)$ of a static quark--antiquark pair at
infinite separation have been computed on the lattice by Kaczmarek and
Zantow~\cite{KZ2005a,KZ2005b} for $N_f = 2$ QCD with
$T_c = 200$~MeV.  These quantities satisfy
\begin{equation}
F_{\infty}(T) = U_{\infty}(T) - T\,S_{\infty}(T).
\end{equation}

The static Landauer ratio for this system is
\begin{equation}
\label{eq:RL_qcd}
\mathcal{R}_L^{\mathrm{QCD}}(T) = \frac{U_{\infty}(T)}{T\,S_{\infty}(T)}.
\end{equation}

\subsection{Lattice data}

We use the data from Table~I of Ref.~\cite{KZ2005a}:
$S_{\infty}(T)$ (dimensionless) and $U_{\infty}(T)/T_c$
(dimensionless) at 16 temperatures spanning $0.79 \leq T/T_c \leq 2.99$.
Table~\ref{tab:qcd_rl} presents the computed $\mathcal{R}_L$.

\begin{table}[t]
\centering
\caption{Static Landauer ratio for QCD flux tubes.
Data from Kaczmarek and Zantow~\cite{KZ2005a}, $N_f = 2$,
$T_c = 200$~MeV.  $N_{\mathrm{bits}} = S_{\infty}/\ln 2$.}
\label{tab:qcd_rl}
\begin{tabular}{@{}rrrrrr@{}}
\toprule
$T/T_c$ & $S_{\infty}$ & $U_{\infty}/T_c$ & $N_{\mathrm{bits}}$ &
$F_{\infty}/T_c$ & $\mathcal{R}_L$ \\
\midrule
0.79 &  5.48 &  9.37 &  7.91 & 5.04 & 2.164 \\
0.84 &  6.49 & 10.19 &  9.36 & 4.74 & 1.868 \\
0.88 &  7.78 & 11.30 & 11.22 & 4.45 & 1.650 \\
0.93 & 12.92 & 15.96 & 18.64 & 3.94 & 1.328 \\
0.98 & 16.38 & 19.27 & 23.63 & 3.22 & 1.200 \\
1.01 & 14.83 & 17.71 & 21.39 & 2.73 & 1.183 \\
1.04 & 12.93 & 15.78 & 18.65 & 2.33 & 1.173 \\
1.09 &  5.49 &  7.84 &  7.92 & 1.86 & 1.310 \\
1.13 &  3.95 &  6.14 &  5.70 & 1.67 & 1.375 \\
1.19 &  2.73 &  4.72 &  3.94 & 1.47 & 1.453 \\
1.29 &  1.63 &  3.37 &  2.35 & 1.27 & 1.603 \\
1.43 &  1.25 &  2.85 &  1.80 & 1.06 & 1.594 \\
1.57 &  1.02 &  2.51 &  1.47 & 0.91 & 1.567 \\
1.72 &  0.91 &  2.32 &  1.31 & 0.76 & 1.483 \\
1.89 &  0.87 &  2.26 &  1.26 & 0.62 & 1.375 \\
2.99 &  0.67 &  2.09 &  0.97 & 0.09 & 1.043 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Results}

Three features stand out:

\begin{enumerate}
\item \textbf{$\mathcal{R}_L > 1$ everywhere.}
At all sampled temperatures, the internal energy exceeds the Landauer
floor.  The QCD flux tube is \emph{super-Landauer}: it stores more
energy per unit information than the thermodynamic minimum.

\item \textbf{Minimum at $T_c$.}
$\mathcal{R}_L$ reaches its minimum value $\approx 1.17$ at
$T/T_c \approx 1.04$, coinciding with the deconfinement phase
transition.  The entropy also peaks near $T_c$
($N_{\mathrm{bits}} \approx 23.6$ at $T/T_c = 0.98$), reflecting the
maximal liberation of color degrees of freedom.

\item \textbf{Deep confinement approaches the black hole value.}
At $T/T_c = 0.79$, $\mathcal{R}_L \approx 2.16$.  This is close to
the Schwarzschild value $\mathcal{R}_L = 2$ (Eq.~\ref{eq:RL_BH}),
placing deep QCD confinement in the same thermodynamic family as
black holes.
\end{enumerate}

The free energy $F_{\infty}$ is positive below $T_c$ and decreasing
above $T_c$, consistent with the standard picture: confinement
requires positive free energy (work must be done to separate quarks),
while above $T_c$ color screening reduces the separation cost.

\subsection{Physical interpretation}

The deconfinement transition is the point where the QCD system most
closely approaches $\mathcal{R}_L = 1$.  At $T_c$, the system
undergoes a reorganization of its information-storage structure from
one-dimensional (flux tube, $d=1$) to zero-dimensional (screened,
quasi-pointlike color charges, $d=0$).

The proximity of QCD deep confinement ($\mathcal{R}_L \approx 2.16$)
to the Schwarzschild black hole ($\mathcal{R}_L = 2$) is striking.
Both systems confine information behind a boundary (the horizon for
gravity, the flux tube for color) and both store roughly twice the
Landauer minimum energy per bit of confined information.  The Smarr
factor of 2 for black holes arises from the homogeneity of the mass
as a function of area ($M \propto A^{1/2}$, giving
$M = 2\,\partial M/\partial S \cdot S = 2TS$); the QCD factor
$\approx 2$ in deep confinement reflects the analogous energetic
overhead of maintaining the chromoelectric string.


% ============================================================
\section{Thermal Casimir effect: \texorpdfstring{$\mathcal{R}_L$}{RL} in the entropic regime}
\label{sec:casimir}

\subsection{Setup}

The Casimir free energy per unit area between two perfectly conducting
plates separated by distance $a$ at temperature $T$ interpolates
between a quantum regime ($\tau \ll 1$) and a classical regime
($\tau \gg 1$), where the dimensionless temperature is
\begin{equation}
\tau \equiv \frac{2\pi a k_B T}{\hbar c}.
\end{equation}

\subsection{Zero-temperature limit}

At $T = 0$, the Casimir energy is purely quantum mechanical:
\begin{equation}
\frac{F_0}{A} = -\frac{\pi^2 \hbar c}{720\, a^3}.
\end{equation}
The entropy vanishes ($S = 0$), so $F = U = F_0$ and $\mathcal{R}_L$
is undefined (no information content to erase).

\subsection{High-temperature (classical) limit}

For $\tau \gg 1$, the free energy becomes~\cite{Lifshitz1956}
\begin{equation}
\frac{F}{A} \to -\frac{\zeta(3)\, k_B T}{8\pi a^2},
\end{equation}
which is purely linear in $T$.  The entropy per unit area is
\begin{equation}
\frac{S}{A} = -\frac{1}{A}\frac{\partial F}{\partial T}
= \frac{\zeta(3)\, k_B}{8\pi a^2},
\end{equation}
and the internal energy is
\begin{equation}
\frac{U}{A} = \frac{F}{A} + T\frac{S}{A} = 0.
\end{equation}

The Casimir free energy in the high-$T$ limit is \emph{entirely
entropic}: $F = -TS$, $U = 0$.  The static Landauer ratio is
therefore
\begin{equation}
\mathcal{R}_L^{\mathrm{Casimir}} = \frac{U}{T S} \to 0
\qquad (\tau \gg 1).
\end{equation}

\subsection{Interpretation}

The thermal Casimir effect is \emph{sub-Landauer}: the system stores
less energy per unit information than the Landauer floor.  In fact, it
stores \emph{no} internal energy at all; the entire free energy
arises from the entropy of suppressed electromagnetic modes between
the plates.

This makes the Casimir effect the thermodynamic opposite of QCD
confinement and black holes:
\begin{itemize}
\item \textbf{QCD and BH}: $\mathcal{R}_L \approx 2$.  Internal
energy dominates.  The confining system stores roughly twice the
Landauer minimum.
\item \textbf{Casimir}: $\mathcal{R}_L \to 0$.  Entropy dominates.
The force is driven purely by the information cost of boundary
conditions, with no stored energy.
\end{itemize}

The crossover from quantum ($U$-dominated) to classical
($S$-dominated) Casimir behavior occurs at $\tau \sim 1$, i.e.,
\begin{equation}
T_{\mathrm{cross}} = \frac{\hbar c}{2\pi a k_B}.
\end{equation}
For plate separation $a = 1~\mu\mathrm{m}$, $T_{\mathrm{cross}} \approx 1150$~K.
As the system crosses from quantum to classical, $\mathcal{R}_L$
decreases from above unity to zero, passing through
$\mathcal{R}_L = 1$ at an intermediate temperature.


% ============================================================
\section{Unified classification}
\label{sec:classification}

Table~\ref{tab:classification} collects the static $\mathcal{R}_L$
values across all systems studied in Papers~C and~D.

\begin{table}[t]
\centering
\caption{Static Landauer ratio $\mathcal{R}_L = U/(TS)$ across
physical systems.}
\label{tab:classification}
\begin{tabular}{@{}llll@{}}
\toprule
System & $\mathcal{R}_L$ & Regime & Source \\
\midrule
QCD, deep confinement & 2.16 & Super & Lattice \\
Schwarzschild BH      & 2    & Super & Smarr \\
QCD, at $T_c$         & 1.17 & Super & Lattice \\
QCD, $T/T_c = 2.99$   & 1.04 & Super & Lattice \\
\midrule
Cosmological apparent  & 1    & Saturating & Misner--Sharp \\
\midrule
Casimir, high-$T$      & 0    & Sub & Exact \\
\bottomrule
\end{tabular}
\end{table}

The classification has three regimes:

\begin{enumerate}
\item \textbf{Super-Landauer} ($\mathcal{R}_L > 1$): Systems that
confine information behind a boundary.  Both the Schwarzschild black
hole ($\mathcal{R}_L = 2$, exact) and QCD deep confinement
($\mathcal{R}_L \approx 2.16$) fall in this regime.  The
near-coincidence of these values, despite the vastly different
physical scales, reflects a shared thermodynamic structure: both
systems store roughly twice the minimum energy per bit of confined
information.

\item \textbf{Landauer-saturating} ($\mathcal{R}_L = 1$):
The cosmological apparent horizon, where the Misner--Sharp energy
exactly equals the entropy-weighted temperature.

\item \textbf{Sub-Landauer} ($\mathcal{R}_L < 1$): Entropy-dominated
systems.  The high-$T$ Casimir effect reaches $\mathcal{R}_L = 0$
(purely entropic free energy, no stored internal energy).
\end{enumerate}

\subsection{Relation to Paper~C}

Paper~C~\cite{Rahnama2026BlackHole} defined a \emph{differential}
Landauer ratio $\mathcal{R}_L^{\mathrm{diff}} = \delta E/(T\,\delta S)$
for thermodynamic processes at horizons.  The differential ratio gives
$\mathcal{R}_L^{\mathrm{diff}} = 1$ for black hole evaporation
(from the first law $dM = T_H\,dS_{BH}$) and
$\mathcal{R}_L^{\mathrm{diff}} = 1/2$ for the cosmological apparent
horizon (from Trivedi's quasi-local energy
accounting~\cite{Trivedi2024}).

The static ratio defined here, $\mathcal{R}_L = U/(TS)$, measures a
different quantity: the total energy budget relative to total
information content, rather than the marginal cost per bit during a
process.  The two are related by the Euler (Smarr) relation.  For
Schwarzschild, the Smarr homogeneity factor gives
$U/(TS) = 2 \times dE/(T\,dS) = 2 \times 1 = 2$.  For the
cosmological horizon,
$U/(TS) = 2 \times \mathcal{R}_L^{\mathrm{diff}} = 2 \times 1/2 = 1$.

Both definitions are valid diagnostics.  The differential ratio is
natural for dynamic processes (evaporation, expansion); the static
ratio is natural for comparing equilibrium systems (QCD, Casimir)
where no process is involved.


% ============================================================
\section{QCD string tension from the Landauer framework}
\label{sec:string_tension}

The storage-dimension scaling argument predicts that $d=1$ storage
(a flux tube) produces a constant force, i.e., a linear potential
$\Phi(r) = \sigma r$ with string tension $\sigma$.  Within the
Landauer framework, the string tension is related to the
information density along the tube:
\begin{equation}
\label{eq:sigma_landauer}
\sigma = k_B T_c \ln 2 \;\cdot\; \rho_{1D},
\end{equation}
where $\rho_{1D}$ is the number of bits per unit length stored in
the flux tube at the deconfinement scale $T_c$.

Using the standard lattice value $\sigma \approx 0.89$~GeV/fm and
the Kaczmarek--Zantow $T_c = 200$~MeV:
\begin{equation}
\rho_{1D} = \frac{\sigma}{T_c \ln 2}
= \frac{0.89}{0.200 \times 0.693}
\approx 6.4~\text{bits/fm}.
\end{equation}

With the modern (2+1)-flavor value $T_c = 155$~MeV:
\begin{equation}
\rho_{1D} \approx \frac{0.89}{0.155 \times 0.693}
\approx 8.3~\text{bits/fm}.
\end{equation}

These values exceed the bare color content of a quark
($\log_2 3 \approx 1.58$~bits), which is expected: the flux tube
carries not only color quantum numbers but also gluonic excitations
that contribute additional information content.

As a cross-check, the L\"uscher correction to the string tension
from bosonic string fluctuations is~\cite{Luscher2002}
\begin{equation}
\sigma_{\mathrm{eff}}(r) = \sigma - \frac{\pi \hbar c}{12\, r^2}.
\end{equation}
At $r = 1$~fm, $\pi \hbar c / 12 \approx 0.052$~GeV$\cdot$fm,
giving a correction of order $6\%$ of $\sigma$, consistent with the
flux tube being a physical one-dimensional object whose
information content is dominated by the zeroth-order string tension.

We emphasize that Eq.~\eqref{eq:sigma_landauer} is not a derivation
of $\sigma$.  It is a consistency check: given the measured string
tension and critical temperature, the implied information density is
physically reasonable (a few bits per fermi, exceeding the bare color
content).


% ============================================================
\section{Perturbative high-temperature limit}
\label{sec:perturbative}

At asymptotically high temperatures, QCD perturbation theory predicts
the leading-order behavior of the internal energy and entropy of the
static $q\bar{q}$ system~\cite{KZ2005a,Kaczmarek2007}:
\begin{align}
U_{\infty}(T) &\sim \mathcal{O}(g^5 T), \\
T\,S_{\infty}(T) &\sim \mathcal{O}(g^3 T),
\end{align}
where $g$ is the QCD coupling.  The static Landauer ratio
therefore scales as
\begin{equation}
\mathcal{R}_L^{\mathrm{QCD}}(T)
= \frac{U_{\infty}}{T\,S_{\infty}}
\sim \frac{g^5 T}{g^3 T}
= g^2(T)
\xrightarrow{T \to \infty} 0,
\end{equation}
by asymptotic freedom ($g \to 0$ as $T \to \infty$).

This means the QCD $\mathcal{R}_L$ must cross through unity at some
temperature above $T_c$.  The lattice data show
$\mathcal{R}_L = 1.04$ at $T/T_c = 2.99$, so the crossing
$\mathcal{R}_L = 1$ occurs at $T/T_c \gtrsim 3$.

The physical picture is clear: at very high temperatures, the QCD
system transitions from a super-Landauer confined regime (flux tube
storing excess energy) to a sub-Landauer screened regime
(color-screened charges with entropy-dominated free energy), passing
through Landauer saturation at an intermediate temperature.  This
mirrors the Casimir quantum-to-classical crossover, where
$\mathcal{R}_L$ also decreases from above to below unity as
thermal effects dominate.


% ============================================================
\section{Cross-consistency with Papers~A, B, and C}
\label{sec:cross}

The results of this paper are consistent with the trilogy framework:

\begin{enumerate}
\item \textbf{Paper~A}~\cite{Rahnama2026A}: The Landauer bound
$Q \geq k_B T \ln 2$ per bit, which appears in the denominator of
$\mathcal{R}_L$, is derived operationally in Paper~A as the minimum
heat generated by quantum measurement.

\item \textbf{Paper~B}~\cite{Rahnama2026BornRule}: The Born rule
emerges from maximizing information yield per Landauer cost.
$\mathcal{R}_L$ measures whether a physical system achieves this
optimal cost in its thermodynamic bookkeeping.

\item \textbf{Paper~C}~\cite{Rahnama2026BlackHole}: The differential
$\mathcal{R}_L$ diagnostic is defined for gravitational horizons.
The present paper extends the analysis to non-gravitational
systems using the static ratio, and relates the two definitions
through the Smarr homogeneity factor
(Section~\ref{sec:classification}).

\item \textbf{Storage dimension and holography}: The $d=0$ case of
the storage-dimension scaling argument reproduces the holographic
scaling $S \propto A$ that underlies the Bekenstein--Hawking entropy.
The static $\mathcal{R}_L = 2$ for black holes follows from combining
this holographic storage with the Smarr relation.
\end{enumerate}


% ============================================================
\section{Scope: what this paper does and does not claim}
\label{sec:scope}

\textbf{What we claim:}
\begin{enumerate}
\item The static Landauer ratio $\mathcal{R}_L = U/(TS)$ is a useful
diagnostic for comparing the energy budgets of thermodynamic systems.
\item QCD flux tubes are super-Landauer ($\mathcal{R}_L > 1$), with
a minimum at $T_c$ and a deep-confinement value
$\mathcal{R}_L \approx 2.16$ close to the Schwarzschild value of 2.
\item The high-$T$ Casimir effect is sub-Landauer
($\mathcal{R}_L \to 0$), computed from exact analytical results.
\item The storage-dimension scaling argument provides a geometric
classification of force laws by information-storage dimensionality.
\item The implied flux-tube information density ($6$--$8$~bits/fm) is
consistent with QCD phenomenology.
\end{enumerate}

\textbf{What we do not claim:}
\begin{enumerate}
\item We do not derive coupling constants, the QCD string tension,
or the fine structure constant from the Landauer framework.
\item We do not modify QCD, QED, or general relativity.
\item We do not claim that information storage ``causes'' forces.
The storage-dimension scaling argument classifies force-law forms by
geometry; it does not provide a dynamical mechanism.
\item We do not claim that the near-coincidence
$\mathcal{R}_L^{\mathrm{QCD}} \approx \mathcal{R}_L^{\mathrm{BH}}
\approx 2$ implies a dynamical connection between QCD confinement
and gravity.  It is a thermodynamic observation that may or may not
have deeper significance.
\item The Kaczmarek--Zantow data use $N_f = 2$ with heavier-than-physical
quark masses.  The qualitative features (minimum at $T_c$,
$\mathcal{R}_L > 1$) are expected to persist for physical quark
masses, but the precise values will shift.
\end{enumerate}


% ============================================================
\section{Conclusion}
\label{sec:conclusion}

We have defined the static Landauer ratio $\mathcal{R}_L = U/(TS)$
and computed it for QCD flux tubes and the thermal Casimir effect.
Combined with gravitational systems, the results define a
three-regime classification:

\begin{enumerate}
\item \textbf{Super-Landauer} ($\mathcal{R}_L \geq 2$):
Schwarzschild black holes ($\mathcal{R}_L = 2$, exact via Smarr) and
QCD deep confinement ($\mathcal{R}_L \approx 2.16$).  Both systems
confine information behind a boundary and store roughly twice the
Landauer minimum energy per bit.

\item \textbf{Landauer-saturating} ($\mathcal{R}_L = 1$):
The cosmological apparent horizon, where the Misner--Sharp energy
exactly equals the entropy-weighted temperature.

\item \textbf{Sub-Landauer} ($\mathcal{R}_L < 1$):
High-temperature Casimir ($\mathcal{R}_L \to 0$) and, at
asymptotically high temperatures, the screened QCD regime
($\mathcal{R}_L \sim g^2 \to 0$).
\end{enumerate}

The storage-dimension scaling argument provides a geometric
organizing principle: $d$-dimensional information storage produces a
force law $F \sim r^{d-2}$, connecting the inverse-square law
($d=0$), confinement ($d=1$), and linear restoring forces ($d=2$) to
the dimensionality of the information-carrying manifold.

The headline result is that black holes and QCD confinement share the
same static Landauer ratio ($\mathcal{R}_L \approx 2$), despite
operating at vastly different scales.  Both systems confine
information and both pay roughly twice the thermodynamic minimum to
do so.

The companion simulation verifies all numerical claims through
70 falsifiable checks across 8 groups, including negative tests that
confirm wrong inputs produce wrong outputs.

\section*{Code Availability}
The supplementary simulation code and generated consistency reports
are available at
\url{https://github.com/MosesRahnama/paper-d-landauer-beyond-horizons}.

\begin{thebibliography}{99}

\bibitem{Landauer1961}
R.~Landauer, ``Irreversibility and Heat Generation in the Computing
Process,''
IBM J.\ Res.\ Dev.\ \textbf{5}, 183 (1961).

\bibitem{Cortes2024}
M.~Cort\^es and A.~R.~Liddle, ``Hawking evaporation and the
Landauer Principle,''
Phys.\ Rev.\ Lett.\ \textbf{132}, 141501 (2024).

\bibitem{Rahnama2026BlackHole}
M.~Rahnama, ``Black Holes as Landauer-Saturating Erasure Channels:
Horizon Diagnostics, Area Quantization, and the Measurement
Complement,''
Preprints (2026), submitted.

\bibitem{Trivedi2024}
A.~Trivedi, ``Landauer's principle and information at the
cosmological horizon,''
arXiv:2407.15231v3 (2024).

\bibitem{Smarr1973}
L.~Smarr, ``Mass Formula for Kerr Black Holes,''
Phys.\ Rev.\ Lett.\ \textbf{30}, 71 (1973).

\bibitem{KZ2005a}
O.~Kaczmarek and F.~Zantow, ``Static quark--antiquark interactions
at zero and finite temperature QCD.\ II.\ Quark--antiquark internal
energy and entropy,''
arXiv:hep-lat/0506019 (2005).

\bibitem{KZ2005b}
O.~Kaczmarek and F.~Zantow, ``Static quark--antiquark interactions
in zero and finite temperature QCD.\ I.\ Heavy quark free energies,
running coupling, and quarkonium binding,''
Phys.\ Rev.\ D \textbf{71}, 114510 (2005),
arXiv:hep-lat/0503017.

\bibitem{Kaczmarek2007}
O.~Kaczmarek, ``Screening at finite temperature and density,''
PoS CPOD07, 043 (2007),
arXiv:0710.0498.

\bibitem{Casimir1948}
H.~B.~G.~Casimir, ``On the attraction between two perfectly
conducting plates,''
Proc.\ K.\ Ned.\ Akad.\ Wet.\ \textbf{51}, 793 (1948).

\bibitem{Lifshitz1956}
E.~M.~Lifshitz, ``The theory of molecular attractive forces between
solids,''
Sov.\ Phys.\ JETP \textbf{2}, 73 (1956).

\bibitem{Luscher2002}
M.~L\"uscher and P.~Weisz, ``Quark confinement and the bosonic
string,''
JHEP \textbf{07}, 049 (2002),
arXiv:hep-lat/0207003.

\bibitem{Bekenstein1973}
J.~D.~Bekenstein, ``Black holes and entropy,''
Phys.\ Rev.\ D \textbf{7}, 2333 (1973).

\bibitem{Hawking1975}
S.~W.~Hawking, ``Particle creation by black holes,''
Commun.\ Math.\ Phys.\ \textbf{43}, 199 (1975).

\bibitem{Rahnama2026A}
M.~Rahnama, ``Calorimetric Signature of Quantum Measurement: A
Record-Formation Heat Bound and Differential Microcalorimetry Test,''
Preprints \textbf{2026}, 202602.1739 (2026).
\url{https://doi.org/10.20944/preprints202602.1739.v2}.

\bibitem{Rahnama2026BornRule}
M.~Rahnama, ``Born's Rule from Record-Formation Constraints: A
Thermodynamic-Information Axiomatics,''
Preprints \textbf{2026}, 202603.0473 (2026).
\url{https://doi.org/10.20944/preprints202603.0473.v1}.

\bibitem{Jacobson1995}
T.~Jacobson, ``Thermodynamics of spacetime: The Einstein equation
of state,''
Phys.\ Rev.\ Lett.\ \textbf{75}, 1260 (1995).

\bibitem{Verlinde2011}
E.~P.~Verlinde, ``On the origin of gravity and the laws of Newton,''
JHEP \textbf{04}, 029 (2011).

\bibitem{tHooft1993}
G.~'t~Hooft, ``Dimensional reduction in quantum gravity,''
arXiv:gr-qc/9310026 (1993).

\bibitem{Susskind1995}
L.~Susskind, ``The world as a hologram,''
J.\ Math.\ Phys.\ \textbf{36}, 6377 (1995).

\end{thebibliography}

\end{document}
